A novel 1000\,MW double-reheat ultra-supercritical system with turbine-extraction-heated air preheaters and low-temperature economizers

### 2018-05-04 article.tex
完成对引言部分的修改，继续提交版本

Among the methods of optimzing the thermal cycle of power plant, the double-reheat USC unit is attractiong increasing number of attention and developing rapidly worldwide. 
The double-reheat USC unit is a new generation of USC unit that can improve thermal performance when compared with a single reheat unit. 
According to~\cite{Zhao2017Exergy}, a double-reheat unit with the inlet parameter 30.0\,MPa/600/620/620$^\circ$C improves the heat efficiency by 2.4\%-2.6\% when compared with a commonly used USC unit with the inlet parameter 25.0\,MPa/600/600$^\circ$C.
The United States built the first double-reheat unit with the main parameter 34.4 MPa/649/566/566$^\circ$C in the 1960s.
Two 700 MW double-reheat USC units were put into operation in Japan in 1990. 
The process of building five double-reheat USC units began in China in 2012, and three of these units were put into operation in 2015.

@@

Liu et al.~\cite{Liu2017} investigated a 660 MW double-reheat unit and calculated the coal consumption decrease if the overheats of No.5 to No.10 extractions could be recovered.
Wang et al.~\cite{Wang2016} studied 1000MW double-reheat USC system adopting outer steam coolers to utilize the superheat of extraction steam and the influence of different extraction schemes on system efficiency.
The results showed that the AOC is an effective method of reducing the superheat degree and improving the efficiency of the unit.
Li et al.~\cite{Li2014Thermodynamic} proposed a system that uses ten-stage extractions and two outer steam coolers. 
The results of the thermodynamic and technical-economic analyses showed that this system can lower the cost of electricity to 55.89 USD/MWh.
In addition, Kjaer~\cite{Kjaer2010A} proposed a regenerative steam turbine for utilizing the superheat degree of the extractions.
In this design, part of the extraction from the turbine high pressure cylinder enters the additional regenerative steam turbine rather than the regenerative heater.
Extractions from the turbine intermediate pressure cylinder are replaced by those from the regenerative steam turbine.
The superheat degree of the extraction is significantly reduced in this design and the exergy destruction of regenerative heaters is likewise reduced, thereby resulting in an overall improvement in efficiency.
Xu et al.~\cite{Xu2015Optimum} compared two superheat utilization systems, one is with additional outer steam cooler (AOC) and the other one is with regenerative steam turbine.
The results showed that the system with regenerative steam turbine had a better techno-economic performance.
Although the above research can make use of extractions' high superheat degree, the loss in the regenerative subsystem is still very large.

@@

The existing research of boiler flue gas heating feedwater has realized the matching of flue gas temperature and feedwater temperature.
In order to further optimize the system, the exergy analytical method is applied to the double reheat USC system by some researchers.
Zhao Z et al.~\cite{Zhao2017Exergy} studied the exergy distribution system for a 1000\,MW double-reheat USC power plant and determined the main causes of exergy destruction on the steam turbine.
Rashidi et al.~\cite{Rashidi2014Thermodynamic} performed a thermodynamic analysis of a double-reheat steam power plant.
According to Ref.~\cite{Wu2014Component}, component- and process-based exergy evaluations were performed on a coal-fired power plant in China, thereby helping researchers to identify energy-saving strategies.
It was pointed out that the exergy destruction in the heat transfer process accounts for the largest proportion of exergy destruction overall.
The largest part of the exergy loss is boiler, and the exergy loss of boiler's air preheater is equivalent to that of the whole regenerative subsystem.
Reducing the loss of air preheater is the key to improve the system's efficiency.

In this paper, the heat exchanging temperature match of air, turbine extractions, boiler economizer outlet flue gas and feedwater was fist proposed based on the existing researchof boiler flue gas heating feedwater, which could reduce the exergy loss of boiler and improve system efficiency.
This is remarkable effect for the double reheat thermal system. 
A novel system based on a 1000\,MW double-reheat USC reference system is proposed to realize boiler and regenerative system energy cascade utilization. 
The novel system realized the reasonable temperature-matching of flue gas, air, extraction steam, and condensate water by using turbine-extraction-heating air preheaters (EAPHs) and low temperature economizer (LTEs).
Specifically, this study included the following tasks: (1) modeling the novel system and reference system with EBSILON® Professional; (2) using exergy analysis to compare both systems' exergy efficiency, exergy destruction distribution, and subsystem performance change; and (3) analyzing both systems' thermal performances under off-design conditions.

>>>>

Among the methods of optimzing the thermal cycle of power plant, the double-reheat USC unit is attractiong increasing number of attention and developing rapidly worldwide. 
The double-reheat USC unit is a new generation of USC unit that can improve thermal performance when compared with a single reheat unit. 
According to~\cite{Zhao2017Exergy}, a double-reheat unit with the inlet parameter 30.0\,MPa/600/620/620$^\circ$C improves the heat efficiency by 2.4\%-2.6\% when compared with a commonly used USC unit with the inlet parameter 25.0\,MPa/600/600$^\circ$C.
The United States built the first double-reheat unit with the main parameter 34.4 MPa/649/566/566$^\circ$C in the 1960s.
Two 700\,MW double-reheat USC units were put into operation in Japan in 1990. 
The process of building five double-reheat USC units began in China in 2012, and three of these units were put into operation in 2015.

@@

Liu et al.~\cite{Liu2017} investigated a 660\,MW double-reheat unit and calculated the coal consumption decrease if the overheats of No.5 to No.10 extractions could be recovered.
Wang et al.~\cite{Wang2016} studied 1000\,MW double-reheat USC system adopting outer steam coolers to utilize the superheat of extraction steam and the influence of different extraction schemes on system efficiency.
The results showed that the  outer steam cooler (AOC) is an effective method of reducing the superheat degree and improving the efficiency of the unit.
Li et al.~\cite{Li2014Thermodynamic} proposed a system that used ten-stage extractions and two AOCs. 
The results of the thermodynamic and technical-economic analyses showed that this system can lower the cost of electricity to 55.89 USD/MWh.
In addition, Kjaer~\cite{Kjaer2010A} proposed a regenerative steam turbine for utilizing the superheat degree of the extractions.
In this design, part of the extraction from the turbine high pressure cylinder enters the additional regenerative steam turbine rather than the regenerative heater.
Extractions from the turbine intermediate pressure cylinder are replaced by those from the regenerative steam turbine.
The superheat degree of the extraction was significantly reduced in this design and the exergy destruction of regenerative heaters was likewise reduced, thereby resulting in an overall improvement in efficiency.
Xu et al.~\cite{Xu2015Optimum} compared two superheat utilization systems, one was with additional AOCs and the other one was with regenerative steam turbine.
The results showed that the system with regenerative steam turbine had a better techno-economic performance.
Although the above research can make use of extractions' high superheat degree, the loss in the regenerative subsystem is still very large.

@@

The existing research of boiler flue gas heating feedwater has realized the matching of flue gas temperature and feedwater temperature.
In order to further optimize the system, the exergy analytical method is applied to the double reheat USC system by some researchers.
Zhao et al.~\cite{Zhao2017Exergy} studied the exergy distribution system for a 1000\,MW double-reheat USC power plant and determined the main causes of exergy destruction on the steam turbine.
Rashidi et al.~\cite{Rashidi2014Thermodynamic} performed a thermodynamic analysis of a double-reheat steam power plant.
According to Ref.~\cite{Wu2014Component}, component- and process-based exergy evaluations were performed on a coal-fired power plant in China, thereby helping researchers to identify energy-saving strategies.
It was pointed out that the exergy destruction in the heat transfer process accounts for the largest proportion of exergy destruction overall.
The largest part of the exergy loss is boiler, and the exergy loss of boiler's air preheater is equivalent to that of the whole regenerative subsystem.
Reducing the loss of air preheater is the key to improve the system's efficiency.

In this paper, the temperature match of air, turbine extractions, boiler economizer outlet flue gas and feedwater was fist proposed based on the existing research of boiler flue gas heating feedwater, which could reduce the exergy loss of boiler and much more effective for the double reheat thermal system.
A novel system based on a 1000\,MW double-reheat USC reference system is proposed to realize boiler and regenerative system energy cascade utilization. 
The novel system realized the reasonable temperature-matching of flue gas, air, extraction steam, and condensate water by using turbine-extraction-heating air preheaters (EAPHs) and low temperature economizer (LTEs).
Specifically, this study included the following tasks: (1) modeling the novel system and reference system with EBSILON® Professional; (2) using exergy analysis to compare both systems' exergy efficiency, exergy destruction distribution, and subsystem performance change; and (3) analyzing both systems' thermal performances under off-design conditions.
